### 2023-02-07 definitions.tex
cleaning up prop 23

%\"Ozkan
\begin{proposition} \cite{DBLP:conf/gg/Ozkan22}
goes on to prove that for finite-branching WSTS with strong monotonicity, a basis of $\uparrow \post^*(s)$ is computable for every given state $s$ iff the downward-closed problem is decidable, i.e. given a state $s$ of a WSTS
% in the regarded class 
with strong monotonicity 
and a decidable downward-closed set $J$, it can be decided whether $\exists s' \in J ~ s \to^* s'$ (Proposition~1 in \cite{DBLP:conf/gg/Ozkan22}). 
\end{proposition}

The characterization is used to show that Petri nets are $\post^*$-effective. It is well-known that Petri nets constitute WSTS with strong monotonicity (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}). Hence Resilience is decidable for Petri nets and VASS.
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the general WSTS framework.

>>>>

%\"Ozkan
\begin{proposition}[Proposition 1 in \cite{DBLP:conf/gg/Ozkan22}]
For finite-branching WSTS with strong upward compatibility, a basis of $\uparrow \post^*(s)$ is computable for every given state $s$ iff the downward-closed problem is decidable, i.e. given a state $s$ of a WSTS
% in the regarded class 
with strong upward compatibility 
and a decidable downward-closed set $J$, it can be decided whether $\exists s' \in J ~ s \to^* s'$. 
\end{proposition}

The characterization is used to show that Petri nets are $\post^*$-effective. It is well-known that Petri nets constitute WSTS with strong upward compatibility (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}). Hence Resilience is decidable for Petri nets and VASS.
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the general WSTS framework.
